Cross-Dataset Recommender System for \\Overcoming Selection Bias

### 2022-08-23 paper/paper.tex
Add a booktab table
Write section 4

\section{Related Work}
Prior works on overcoming selection bias-induced distribution shift via a propensity-based approach begins with the seminal paper \cite{schnabel2016recommendations}, which introduces the IPS method into recommender systems. Follow-up works aim at providing a learning-based or behavioral model of user feedbacks for propensity estimation \cite{joachims2017unbiased} \cite{yang2018unbiased}, which remains the central concern of this approach. In this work we add to previous attempts the idea of using a more quantized, implicit dataset for more accurate propensity estimation.

@@

Denote the less quantized dataset for training as $D$. We propose the \textbf{naive-bayes propensity estimator} from a more quantized (binary) dataset $D'$. Essentially,
\begin{equation} 
  P_{u,i} = \Pr(Y_{u,i} \text{ is observed} \mid ) = \frac{}{\text{}},
\end{equation}
where xxx.

@@

@@

\begin{table}
  \caption{Test set RMSE and MAE for NBPE-MF and baselines}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule(r){1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\section{Related Work}
Prior works on overcoming selection bias-induced distribution shift via a propensity-based approach begins with the seminal paper \cite{schnabel2016recommendations}, which introduces the IPS method into recommender systems. Follow-up works aim at providing a learning-based or behavioral model of user feedbacks for propensity estimation \cite{joachims2017unbiased} \cite{yang2018unbiased}, which remains the central concern of this approach. While many works rely on a propensity matrix that is assumed to be known, TODO our work provides an idea of using a more quantized, implicit dataset for accurate propensity estimation.

@@

Denote the biased training set as $D$. we propose the \textbf{naive-bayes propensity estimator} from a more quantized (binary) dataset $D'$. Essentially,
\begin{equation} 
  P_{u,i} = \Pr(Y_{u,i} \text{ is observed} \mid Y_{u,i} = r_{u,i}) = \frac{\Pr(Y_{u,i} = r_{u,i} \mid Y_{u,i} \text{ is observed})}{\Pr(Y_{u,i}) = r_{u,i}},
\end{equation}
where the numerator can be easily approximated from the dataset, but the denominator requires additional data from less biased sources. In this paper, we estimates the denominator from the unbiased, more quantized dataset using a categorical naive-bayes model. We use $D'$ as a mask to hide biased ratings in the training set from propensity estimation. In other words, $Y_{u,i} \text{ is considered observed}$ only when $D'_{u,i} \text{ is observed}$. If the corresponding rating is not captured in $D'$, we set its propensity to the average propensity.

@@

\textbf{Mixing Datasets MF.}
Pending

@@

\begin{table}
  \caption{Test set RMSE and MAE for NBPE-MF and baselines}
  \label{sample-table}
  \centering
  \begin{tabular}{lllll}
    \toprule               
            & \multicolumn{2}{c}{ML100K} & \multicolumn{2}{c}{Latent Factors}              \\
    \cmidrule(r){2-5}
            & RMSE                       & MAE                                & RMSE & MAE \\
    \midrule
    MF      & 0                          & 0                                  & 0    & 0   \\ 
    NPE-MF  & 0                          & 0                                  & 0    & 0   \\ 
    NBPE-MF & 0                          & 0                                  & 0    & 0   \\ 
    \bottomrule
  \end{tabular}
\end{table}
